\section{Software Lifecycle}

    \subsection{Why Learn Software Engineering/Development?}

        Investment.

    \subsection{Typical Software Development Lifecycle}

        \begin{enumerate}
            \item Requirements
                \begin{itemize}
                    \item What is going to be built?
                \end{itemize}
            \item Design
                \begin{itemize}
                    \item How is it going to be built?
                \end{itemize}
            \item Implementation
                \begin{itemize}
                    \item Building.
                \end{itemize}
            \item Verification
                \begin{itemize}
                    \item Testing.
                \end{itemize}
            \item Maintence
                \begin{itemize}
                    \item Fixing.
                \end{itemize}
        \end{enumerate}

    \subsection{Software Development Lifecycle Example}

        \begin{enumerate}
            \item Requirements
                \begin{itemize}
                    \item Collect email address and message.
                    \item Send to and store in a database.
                    \item Prevent user from bad input.
                \end{itemize}
            \item Design
                \begin{itemize}
                    \item Use HTML and CSS for building the framework of the form.
                    \item Use Javascript for verification of the input.
                    \item Use JQuery and MYSQL for contacting backend.
                \end{itemize}
            \item Implementation
                \begin{itemize}
                    \item Conde and document the work.
                \end{itemize}
            \item Verification
                \begin{itemize}
                    \item Does the form collect information?
                    \item Does the form send that information to a database?
                    \item Does the form prevent bad user imput?
                \end{itemize}
            \item Maintence
                \begin{itemize}
                    \item Create lifecycle plan, fix any bugs.
                \end{itemize}
        \end{enumerate}