\section{Requirements and Specifications}

    \subsection{Requirements Definition}

        A way of figuring out the exact specifications of what the software should do.

    \subsection{Requirements vs Specifications}
    
        \begin{itemize}
            \item Requirements
            \begin{itemize}
                \item A non-technical definition of something the user requires from the system.
            \end{itemize}
            \item Specifications
            \begin{itemize}
                \item A technical definition of what is required from the system.
            \end{itemize}
        \end{itemize}

    \subsection{Functional vs Non-Functional Requirements}

        \begin{itemize}
            \item Functional
            \begin{itemize}
                \item Requirements and specifications pertaining to the function of the program.
            \end{itemize}
            \item Non-functional
            \begin{itemize}
                \item Requirements and specifications on what goals should be met.
            \end{itemize}
        \end{itemize}

        \begin{itemize}
            \item Non-functional
            \begin{itemize}
                \item Product Requirements
                \begin{itemize}
                    \item Mest have of the product itself. Talk about behavior.
                \end{itemize}
                \item Organizational Requirements
                \begin{itemize}
                    \item Company policies, standards, styles, rules.
                \end{itemize}
                \item External Requirements
                \begin{itemize}
                    \item External laws, regulations, trends etc.
                \end{itemize}
            \end{itemize}
        \end{itemize}

    \subsection{WRSPM Model Introduction}

        \begin{itemize}
            \item World
            \begin{itemize}
                \item The world assumptions which are used to develop the system.
            \end{itemize}
            \item Requirements
            \begin{itemize}
                \item Defining the problem at hand in terms of a user of the system.
            \end{itemize}
            \item Specifications
            \begin{itemize}
                \item Defining the technical requirements of the sysmte. Here we are linking together the idea of the solution, to the system itself.
            \end{itemize}
            \item program
            \begin{itemize}
                \item The program and code itself.
            \end{itemize}
            \item Machine
            \begin{itemize}
                \item Hardware specifications.
            \end{itemize}
        \end{itemize}

    \subsection{WRSPM Visual Model}

        \begin{itemize}
            \item Environment
            \begin{itemize}
                \item World
                \item Requirements
            \end{itemize}
            \item Interface
            \begin{itemize}
                \item Specifications
            \end{itemize}
            \item system
            \begin{itemize}
                \item Program
                \item Machine
            \end{itemize}
        \end{itemize}

    \subsection{WRSPM Variables}

        \begin{itemize}
            \item Environment
            \begin{itemize}
                \item Eh
                \begin{itemize}
                    \item Elements of the environment which are hidden from the system.
                \end{itemize}
            \end{itemize}
            \item Interface
            \begin{itemize}
                \item Ev
                \begin{itemize}
                    \item Elements of the environment which are visible from the system.
                \end{itemize}
                \item Sv
                \begin{itemize}
                    \item Elements of the system which are visible from the environment.
                \end{itemize}
            \end{itemize}
            \item System
            \begin{itemize}
                \item Sh
                \begin{itemize}
                    \item Eelements from the system which are hidden from the environment.
                \end{itemize}
            \end{itemize}
        \end{itemize}

    \subsection{WRSPM - World Example}

        Example: photo machine.

        \begin{itemize}
            \item World Assumptions
            \begin{itemize}
                \item There will be readily available electricity.
                \item There will be internet.
                \item In a normal, controlled, temperature.
                \item Peoplewill have standardized photo formats to print.
                \item Poeple will be able to read the prompts and tutorial.
                \item Sotires will re-fill the materials frequently.
                \item People will have debit cards that wirk with standard debit card tech.
                \item Debit/credit cards are widely used.
            \end{itemize}
        \end{itemize}

    \subsection{WRSPM - Requirements Example}

        Example: photo machine.

        \begin{itemize}
            \item Requirements
            \begin{itemize}
                \item A user can connet a smartphone to the system.
                \item The user can edit photos.
                \item The smartphone can transfer pictures over.
                \item The photos can be printed out of the macinhe.
                \item The kiosk can collect money.
                \item The user can change the language.
            \end{itemize}
        \end{itemize}

    \subsection{WRSPM - Specifications Example}

    Example: photo machine.

    \begin{itemize}
        \item Specifications
        \begin{itemize}
            \item The system will have Bluetooth technology so a smartphone can connect.
            \item The machine will run off a standard NA power outlet.
            \item A proper bluetooth tranfer protocol will be installed to make the transaction secure.
            \item The system will have and editing suite for manipulating photo data.
            \item The system will use encryption and chip technology to contact financial servers.
            \item The system will have a standard printing device for printing photos.
        \end{itemize}
    \end{itemize}

    \subsection{Requirements Example}

    We have already built Chess app. Wewant to monetize this app to start making money. 

    \begin{enumerate}
        \item What steps should we take?
        \item How do we define this problem?
        \item What will benefit both the client and the users?
    \end{enumerate}

    \begin{itemize}
        \item World Assumptions
        \begin{itemize}
            \item There is a way to pay on smartphones.
            \item There are ways to make money from an app.
            \item The app is extendable.
            \item There will be an ability to contact the internet and the financial institution.
            \item The transaction canbe made secure enough.
            \item The phone will have the processing power to process the request.
            \item Different currencies will be able to be accepted.
            \item It's legal to accept payment over a phone.
        \end{itemize}
        \item Requirements
        \begin{itemize}
            \item The pro feature will remove ads for the user.
            \item The feature must accept paument from the user.
            \item The feature must provide pro features upon successful transaction.
            \item The feature must complete transactions is a secure manner.
            \item The feature will revoke pro feautures once a subscription becomes invalid.
            \item The feature will provide a cancel buttun within the app.
            \item The feature will extend off existing database.
            \item The feature musn.t add more than 5MB to overall download size.
            \item The feature must complete the transaction in a timely fashion.
        \end{itemize}
        \item Specifications
        \begin{itemize}
            \item The feature will be coded in Java, the existing app's language.
            \item The feature will use the Android Play store for it's transactions.
            \item The feature will check for active subscription daily using Google's provided API.
            \item The feature will turn off AdMob once subscription key becomes invalid.
            \item The transaction must take no longer than 500ms to complete.
        \end{itemize}
    \end{itemize}
