\documentclass{article}


\title{Sofware Engineering 101: Exercises}
\author{Bernardo Paulsen}

\begin{document}
    
\maketitle

\section{Introduction}

    \subsection{Welcome to the Course!}

\section{Software Lifecycle}

    \subsection{Why Learn Software Engineering/Development?}

        Investment.

    \subsection{Typical Software Development Lifecycle}

        \begin{enumerate}
            \item Requirements
                \begin{itemize}
                    \item What is going to be built?
                \end{itemize}
            \item Design
                \begin{itemize}
                    \item How is it going to be built?
                \end{itemize}
            \item Implementation
                \begin{itemize}
                    \item Building.
                \end{itemize}
            \item Verification
                \begin{itemize}
                    \item Testing.
                \end{itemize}
            \item Maintence
                \begin{itemize}
                    \item Fixing.
                \end{itemize}
        \end{enumerate}

    \subsection{Software Development Lifecycle Example}

        \begin{enumerate}
            \item Requirements
                \begin{itemize}
                    \item Collect email address and message.
                    \item Send to and store in a database.
                    \item Prevent user from bad input.
                \end{itemize}
            \item Design
                \begin{itemize}
                    \item Use HTML and CSS for building the framework of the form.
                    \item Use Javascript for verification of the input.
                    \item Use JQuery and MYSQL for contacting backend.
                \end{itemize}
            \item Implementation
                \begin{itemize}
                    \item Conde and document the work.
                \end{itemize}
            \item Verification
                \begin{itemize}
                    \item Does the form collect information?
                    \item Does the form send that information to a database?
                    \item Does the form prevent bad user imput?
                \end{itemize}
            \item Maintence
                \begin{itemize}
                    \item Create lifecycle plan, fix any bugs.
                \end{itemize}
        \end{enumerate}

\section{Requirements and Specifications}

    \subsection{Requirements Definition}

        A way of figuring out the exact specifications of what the software should do.

    \subsection{Requirements vs Specifications}
    
        \begin{itemize}
            \item Requirements
            \begin{itemize}
                \item A non-technical definition of something the user requires from the system.
            \end{itemize}
            \item Specifications
            \begin{itemize}
                \item A technical definition of what is required from the system.
            \end{itemize}
        \end{itemize}

    \subsection{Functional vs Non-Functional Requirements}

    \begin{itemize}
        \item Functional
        \begin{itemize}
            \item Requirements and specifications pertaining to the function of the program.
        \end{itemize}
        \item Non-functional
        \begin{itemize}
            \item Requirements and specifications on what goals should be met.
        \end{itemize}
    \end{itemize}

    \begin{itemize}
        \item Non-functional
        \begin{itemize}
            \item Product Requirements
            \begin{itemize}
                \item Mest have of the product itself. Talk about behavior.
            \end{itemize}
            \item Organizational Requirements
            \begin{itemize}
                \item Company policies, standards, styles, rules.
            \end{itemize}
            \item External Requirements
            \begin{itemize}
                \item External laws, regulations, trends etc.
            \end{itemize}
        \end{itemize}
    \end{itemize}

    \subsection{WRSPM Model Introduction}

    \begin{itemize}
        \item World
        \begin{itemize}
            \item The world assumptions which are used to develop the system.
        \end{itemize}
        \item Requirements
        \begin{itemize}
            \item Defining the problem at hand in terms of a user of the system.
        \end{itemize}
        \item Specifications
        \begin{itemize}
            \item Defining the technical requirements of the sysmte. Here we are linking together the idea of the solution, to the system itself.
        \end{itemize}
        \item program
        \begin{itemize}
            \item The program and code itself.
        \end{itemize}
        \item Machine
        \begin{itemize}
            \item Hardware specifications.
        \end{itemize}
    \end{itemize}

    \subsection{WRSPM Visual Model}

    \begin{itemize}
        \item Environment
        \begin{itemize}
            \item World
            \item Requirements
        \end{itemize}
        \item Interface
        \begin{itemize}
            \item Specifications
        \end{itemize}
        \item system
        \begin{itemize}
            \item Program
            \item Machine
        \end{itemize}
    \end{itemize}

    \subsection{WRSPM Variables}

    \begin{itemize}
        \item Environment
        \begin{itemize}
            \item Eh
            \begin{itemize}
                \item Elements of the environment which are hidden from the system.
            \end{itemize}
        \end{itemize}
        \item Interface
        \begin{itemize}
            \item Ev
            \begin{itemize}
                \item Elements of the environment which are visible from the system.
            \end{itemize}
            \item Sv
            \begin{itemize}
                \item Elements of the system which are visible from the environment.
            \end{itemize}
        \end{itemize}
        \item System
        \begin{itemize}
            \item Sh
            \begin{itemize}
                \item Eelements from the system which are hidden from the environment.
            \end{itemize}
        \end{itemize}
    \end{itemize}

    \subsection{WRSPM - World Example}
    \subsection{WRSPM - Requirements Example}
    \subsection{WRSPM - Specifications Example}
    \subsection{Requirements Example}





\end{document}